---
title: "code"
output: html_document
---

# Load packages + data
```{r}
library(tidyverse)
library(psych)
library(here)
library(lm.beta)
library(car)
library(caret)
recode <- dplyr::recode

d <- read.csv(here("simulated_data.csv"))
```

# Data Cleaning
```{r}
#First step is to format the csv & delete entries that skipped to the end of the survey
d1 <- d[-(1:2),]
d1 <- d1 %>% 
  filter(Q1 == 1,
         Age != 1,
         US.resident == 1)
#Reverse code
d2 <- d1 %>% 
  mutate_at(c("Attitude...self_3", "Attitude...asylum_3","Attitude...self_5", "Attitude...asylum_5"),
            recode, "1" = 3, "2" = 2, "3" = 1)
d2 <- d2 %>% 
  mutate_at(c("BaseEmpathic.concern_2", "BaseEmpathic.concern_5", "BaseEmpathic.concern_6"),
            recode, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1)
         
#Force character values into numbers
d2[,c(3:6, 11:15, 17:71)] <- d2[,c(3:6, 11:15, 17:71)] %>% 
  mutate_if(is.character, as.numeric) #all questions should be changed to numeric except dates and gender text box 
sapply(d2,class)
#Calculate response time cut-off threshold
#rename and transform response time variable
d2 <- d2 %>%
  rename(stim_time = Duration..in.seconds.)
  #mutate(log_time = log(stim_time)) #log transformations of fake data made odd data
#get mean, sd, and 2 sd outlier threshold for response times
time_m <- mean(d2$stim_time) #with real data, d2$log_time
time_sd <- sd(d2$stim_time) #with real data, d2$log_time
out.u <- time_m + 2*time_sd 
out.l <- time_m - 2*time_sd
#remove outlier response times
d2_outlier <- d2 %>%
  filter(-stim_time<out.u) %>%
  filter(-stim_time>out.l)
# Basic Empathic Concern (BEconcern)
d3 <- d2_outlier
which(colnames(d3) == "BaseEmpathic.concern_1")
alpha(d3[, 27:33])
d3 <- d3%>% 
  mutate(
  BEconcern = rowMeans(select(., c("BaseEmpathic.concern_1", "BaseEmpathic.concern_2","BaseEmpathic.concern_3",
                                 "BaseEmpathic.concern_5", "BaseEmpathic.concern_6", "BaseEmpathic.concern_7"))))
# American Identity (identity)
which(colnames(d3) == "Identif..as.American_1")
alpha(d3[, 34:37])
d3 <- d3%>% 
  mutate(
  identity = rowMeans(select(., c("Identif..as.American_1", "Identif..as.American_2","Identif..as.American_3",
                                 "Identif..as.American_4"))))
#Petition Willingess (petition)
which(colnames(d3) == "activism...petition_1")
alpha(d3[, 38:41])
d3 <- d3%>% 
  mutate(
  petition = rowMeans(select(., c("activism...petition_1", "activism...petition_2","activism...petition_3",
                                 "activism...petition_4"))))
# Activism Donation (donation)
which(colnames(d3) == "activism...donation_1")
alpha(d3[, 42:45])
d3 <- d3%>% 
  mutate(
  donation = rowMeans(select(., c("activism...donation_1", "activism...donation_2","activism...donation_3",
                                 "activism...donation_4"))))
# Donation Value  (donation_value)
d3 <- d3 %>%
  rename(donation_value = donations.amout) %>%
  mutate(donation_value = log(donation_value)) # adjust for wide range of possible donation values
#Empathy check: emotional response questionnaire (ERQ)
which(colnames(d3) == "Emp..Emot..Resp._1")
alpha(d3[, 47:52])
d3 <- d3%>% 
  mutate(
  ERQ = rowMeans(select(., c("Emp..Emot..Resp._1", "Emp..Emot..Resp._2","Emp..Emot..Resp._3",
                                 "Emp..Emot..Resp._4", "Emp..Emot..Resp._5", "Emp..Emot..Resp._6"))))
#Recat check: Attitude/Intergroup_Bias Self (attitude_self)
which(colnames(d3) == "Attitude...self_1")
alpha(d3[, 54:59])
d3 <- d3%>% 
  mutate(
  attitude_self = rowMeans(select(., c("Attitude...self_1", "Attitude...self_2","Attitude...self_3",
                                 "Attitude...self_4", "Attitude...self_5", "Attitude...self_6"))))
#Empathy check: Attitude Asylum (attitude_asylum)
which(colnames(d3) == "Attitude...asylum_1")
alpha(d3[, 60:65])
d3 <- d3%>% 
  mutate(
  attitude_asylum = rowMeans(select(., c("Attitude...asylum_1", "Attitude...asylum_2","Attitude...asylum_3",
                                 "Attitude...asylum_4", "Attitude...asylum_5", "Attitude...asylum_6"))))
#Recat check: Intergroup bias (bias)
d3 <- d3 %>%
  mutate(bias = attitude_asylum - attitude_self) # negative values indicates bias to self; positive indicates bias to asylum
#Demographics - Control Variable
#Keep original: Age, gender, ethnicity, education, employment, region
#Dummy code: 
# political
d3 <- d3 %>% 
  mutate(
    democrat = if_else(Political == 1, 1, 0),
    republican = if_else(Political == 2, 1, 0),
    independent = if_else(Political == 3, 1, 0),
    somethingelse = if_else(Political == 5,1,0),
    dontknow = if_else(Political == 10,1,0)
  )
#previous activism engagement
d3 <- d3 %>% 
  mutate(
    donate_year_yes = if_else(previous.activism_1 == 1, 1, 0),
    donate_year_no = if_else(previous.activism_1 == 2, 1, 0),
    sign_year_yes = if_else(previous.activism_2 == 1, 1, 0),
    sign_year_no = if_else(previous.activism_2 == 2, 1, 0),
    donate_life_yes = if_else(previous.activism_3 == 1, 1, 0),
    donate_life_no = if_else(previous.activism_3 == 2, 1, 0),
    sign_life_yes = if_else(previous.activism_4 == 1, 1, 0),
    sign_life_no = if_else(previous.activism_4 == 2, 1, 0)
  )
# OPTIONAL VARIABLE DATAFRAME
d4 <- d3 %>%
  select(Condition, Q_TotalDuration, Age, US.resident, Region, Gender, Education, Employment, stim_time, donation_value, Recat..IOS.circles, c(72:92))
```
# T-test
1. Each Condition * Control
2. Recat + Empathy * Empathy
3. Recat + Empathy * Recat
```{r}
#FYI, I'm not sure this is the correct/best way to run these t-tests, but I attempted the code!! 

#petition
petition_control <- d3 %>%
  filter(Condition == "1") %>%
  pull(petition)

petition_ID_only <- d3 %>%
  filter(Condition == "2") %>%
  pull(petition)

petition_emp_only <- d3 %>%
  filter(Condition == "3") %>%
  pull(petition)

petition_ID_and_Em <- d3 %>%
  filter(Condition == "4") %>%
  pull(petition)


#petition by control (H1 and H2)
t.test(petition_ID_only, petition_control, alternative = c("greater"), mu=0, paired=FALSE, var.equal = FALSE, conf.level = 0.95)
t.test(petition_emp_only, petition_control, alternative = c("greater"), mu=0, paired=FALSE, var.equal = FALSE, conf.level = 0.95)
t.test(petition_ID_and_Em, petition_control, alternative = c("greater"), mu=0, paired=FALSE, var.equal = FALSE, conf.level = 0.95)
#petition by emp or ID (Not official H, just testing whether one of emp or ID only is significantly larger than the other))
t.test(petition_ID_only, petition_emp_only, alternative = c("greater"), mu=0, paired=FALSE, var.equal=FALSE, conf.level = 0.95)
t.test(petition_emp_only, petition_ID_only, alternative = c("greater"), mu=0, paired=FALSE, var.equal=FALSE, conf.level = 0.95)
#petition by emp+ID (H3)
t.test(petition_ID_and_Em, petition_ID_only, alternative = c("greater"), mu=0, paired=FALSE, var.equal = FALSE, conf.level = 0.95)
t.test(petition_ID_and_Em, petition_emp_only, alternative = c("greater"), mu=0, paired=FALSE, var.equal = FALSE, conf.level = 0.95)
#donation
donat_control <- d3 %>%
  filter(Condition == "1") %>%
  pull(donation)
donat_ID_only <- d3 %>%
  filter(Condition == "2") %>%
  pull(donation)
donat_emp_only <- d3 %>%
  filter(Condition == "3") %>%
  pull(donation)
donat_ID_and_Em <- d3 %>%
  filter(Condition == "4") %>%
  pull(donation)
#donation by control (H1 to H2)
t.test(donat_ID_only, donat_control, alternative = c("greater"), mu=0, paired=FALSE, var.equal = FALSE, conf.level = 0.95)
t.test(donat_emp_only, donat_control, alternative = c("greater"), mu=0, paired=FALSE, var.equal = FALSE, conf.level = 0.95)
t.test(donat_ID_and_Em, donat_control, alternative = c("greater"), mu=0, paired=FALSE, var.equal = FALSE, conf.level = 0.95)
#donation by emp or ID (Not official H, just testing whether one of emp or ID only is significantly larger than the other)
t.test(donat_ID_only, donat_emp_only, alternative = c("greater"), mu=0, paired=FALSE, var.equal = FALSE, conf.level = 0.95)
t.test(donat_emp_only, donat_ID_only, alternative = c("greater"), mu=0, paired=FALSE, var.equal = FALSE, conf.level = 0.95)
#donation by emp+ID (H3)
t.test(donat_ID_and_Em, donat_ID_only, alternative = c("greater"), mu=0, paired=FALSE, var.equal = FALSE, conf.level = 0.95)
t.test(donat_ID_and_Em, donat_emp_only, alternative = c("greater"), mu=0, paired=FALSE, var.equal = FALSE, conf.level = 0.95)
```
# ANOVA: Compare Group Results
1. Post test dependent variables
2. Past activism behavior
3. Manipulation check scores
4. Baseline empathic concern
```{r}
#Option 1
#Compare Group Results: regressions vs ANOVAs - using petition as example DV
Control_and_ID <- d3 %>%
  filter(Condition == "1" | Condition == "2") %>%
  mutate_at(c("Condition"),
            recode, "1" = 0, "2" = 1)

Control_and_empathy <- d3 %>%
  filter(Condition == "1" | Condition == "3") %>%
    mutate_at(c("Condition"),
            recode, "1" = 0, "3" = 1)

Control_and_Emp_ID <- d3 %>%
  filter(Condition == "1" | Condition == "4") %>%
  mutate_at(c("Condition"),
          recode, "1" = 0, "4" = 1)

EmpONLY_vs_EmpANDID <- d3 %>%
  filter(Condition == "3" | Condition == "4") %>%
  mutate_at(c("Condition"),
          recode, "3" = 0, "4" = 1)

IdONLY_vs_EmpANDID <- d3 %>%
  filter(Condition == "3" | Condition == "4") %>%
  mutate_at(c("Condition"),
          recode, "2" = 0, "4" = 1)

#control versus each condition (ID only, emp only, ID+empahty)
reg_petition_1 <- lm(petition~Control_and_ID$Condition, data=Control_and_ID)

summary(reg_petition_1)

reg_petition_2 <- lm(petition~Control_and_empathy$Condition, data=Control_and_empathy)

summary(reg_petition_2)

reg_petition_3 <- lm(petition~Control_and_Emp_ID$Condition, data=Control_and_Emp_ID)

summary(reg_petition_3)

#ID+empathy versus ID only and Emp only
reg_petition_4 <-lm(petition~EmpONLY_vs_EmpANDID$Condition, data=EmpONLY_vs_EmpANDID)

summary(reg_petition_4)

reg_petition_5 <-lm(petition~IdONLY_vs_EmpANDID$Condition, data=IdONLY_vs_EmpANDID)

summary(reg_petition_5)

#Option2
#rercode three columns each condition as the reference group

d3 <- d3 %>% 
  mutate(
    cond1 = factor(Condition, c(1,2,3,4), labels=c('con', 'sup','em', 'supem')))
    
#petition (control as reference group)
lm1a <- lm(petition ~ cond1, data = d3)

summary(lm1a)

#donation (control as rerference group)
lm1b <- lm(donation ~ cond1, data = d3)

summary(lm1b)

#Basic empathic conern (control as rerference group)
lm2 <- lm(BEconcern ~ cond1, data = d3)

summary(lm2)

#American Identity (control as rerference group)
lm3 <- lm(identity ~ cond1, data = d3)

#attitude (control as a referecen gruop)
lm4a <- lm(attitude_self ~ cond1, data = d3)
lm4b <- lm(attitude+asylum ~ cond1, data = d3)


summary(lm3)

##aov(dv~X*Y,data=df)
##m1 <- lm(dv~X+Y,data=df)
##m2 <- lm(dv~X*Y,data=df

```
# Regressions: 
1. check VIF for multicollinearity
2. models


```{r}
# Regressions
# isolate conditions into dfs
d3_1 <- d3 %>%
  filter(Condition=="1")
d3_2 <- d3 %>%
  filter(Condition=="2")
d3_3 <- d3 %>%
  filter(Condition=="3")
d3_4 <- d3 %>%
  filter(Condition=="4")
# model name format: regression // condition // predicting 'p'etition or 'd'onation // predictors
# independent variables: ERQ, attitude_asylum, Recat..IOS.circles, bias
# dependent variables: petition, donation
# control variables: BEconcern democrat republican independent somethingelse dontknow donate_year_yes donate_year_no donate_life_yes donate_life_no sign_year_yes sign_year_no sign_life_yes sign_life_no
  # removed independent, somethingelse, dontknow, and all "..._no" dummy variables do to aliased coefficients
# condition 1: control
# model: dv~iv
reg_1_p_emp <- lm(petition ~ ERQ + attitude_asylum, data = d3_1)
vif(reg_1_p_emp) #remove predictors with large VIFs
summary(reg_1_p_emp)
reg_1_p_id <- lm(petition ~ Recat..IOS.circles + bias, data = d3_1)
vif(reg_1_p_id) 
summary(reg_1_p_id)
reg_1_p <- lm(petition ~ ERQ + attitude_asylum + Recat..IOS.circles + bias, data = d3_1)
vif(reg_1_p)
summary(reg_1_p)
reg_1_d_emp <- lm(donation ~ ERQ + attitude_asylum, data = d3_1)
vif(reg_1_d_emp)
summary(reg_1_d_emp)
reg_1_d_id <- lm(donation ~ Recat..IOS.circles + bias, data = d3_1)
vif(reg_1_d_id)
summary(reg_1_d_id)
reg_1_d <- lm(donation ~ ERQ + attitude_asylum + Recat..IOS.circles + bias, data = d3_1)
vif(reg_1_d)
summary(reg_1_d)
#model: dv~iv+cv
reg_1_p_emp_c <- lm(petition ~ ERQ + attitude_asylum + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_1) 
vif(reg_1_p_emp_c)
summary(reg_1_p_emp_c)
reg_1_p_id_c <- lm(petition ~ Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_1)
vif(reg_1_p_id_c)
summary(reg_1_p_id_c)
reg_1_p_c <- lm(petition ~ ERQ + attitude_asylum + Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_1)
vif(reg_1_p_c)
summary(reg_1_p_c)
reg_1_d_emp_c<- lm(donation ~ ERQ + attitude_asylum + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_1)
vif(reg_1_d_emp_c)
summary(reg_1_d_emp_c)
reg_1_d_id_c <- lm(donation ~ Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_1)
vif(reg_1_d_id_c)
summary(reg_1_d_id_c)
reg_1_d_c <- lm(donation ~ ERQ + attitude_asylum + Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_1)
vif(reg_1_d_c)
summary(reg_1_d_c)
# condition 2: ID only
# model: dv~iv
reg_2_p_emp <- lm(petition ~ ERQ + attitude_asylum , data = d3_2)
vif(reg_2_p_emp)
summary(reg_2_p_emp)
reg_2_p_id <- lm(petition ~ Recat..IOS.circles + bias, data = d3_2)
vif(reg_2_p_id)
summary(reg_2_p_id)
reg_2_p <- lm(petition ~ ERQ + attitude_asylum + Recat..IOS.circles + bias, data = d3_2)
vif(reg_2_p)
summary(reg_2_p)
reg_2_d_emp <- lm(donation ~ ERQ + attitude_asylum, data = d3_2)
vif(reg_2_d_emp)
summary(reg_2_d_emp)
reg_2_d_id <- lm(donation ~ Recat..IOS.circles + bias, data = d3_2)
vif(reg_2_d_id)
summary(reg_2_d_id)
reg_2_d <- lm(donation ~ ERQ + attitude_asylum + Recat..IOS.circles + bias, data = d3_2)
vif(reg_2_d)
summary(reg_2_d)
# model: dv~iv+cv
reg_2_p_emp_c <- lm(petition ~ ERQ + attitude_asylum + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_2)
vif(reg_2_p_emp_c)
summary(reg_2_p_emp_c)
reg_2_p_id_c <- lm(petition ~ Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_2)
vif(reg_2_p_id_c)
summary(reg_2_p_id_c)
reg_2_p_c <- lm(petition ~ ERQ + attitude_asylum + Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_2)
vif(reg_2_p_c)
summary(reg_2_p_c)
reg_2_d_emp_c <- lm(donation ~ ERQ + attitude_asylum + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_2)
vif(reg_2_d_emp_c)
summary(reg_2_d_emp_c)
reg_2_d_id_c <- lm(donation ~ Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_2)
vif(reg_2_d_id_c)
summary(reg_2_d_id_c)
reg_2_d_c <- lm(donation ~ ERQ + attitude_asylum + Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_2)
vif(reg_2_d_c)
summary(reg_2_d_c)
# condition 3: empathy only
reg_3_p_emp <- lm(petition ~ ERQ + attitude_asylum, data = d3_3)
vif(reg_3_p_emp)
summary(reg_3_p_emp)
reg_3_p_id <- lm(petition ~ Recat..IOS.circles + bias, data = d3_3)
vif(reg_3_p_id)
summary(reg_3_p_id)
reg_3_p <- lm(petition ~ ERQ + attitude_asylum + Recat..IOS.circles + bias, data = d3_3)
vif(reg_3_p)
summary(reg_3_p)
reg_3_d_emp <- lm(donation ~ ERQ + attitude_asylum, data = d3_3)
vif(reg_3_d_emp)
summary(reg_3_d_emp)
reg_3_d_id <- lm(donation ~ Recat..IOS.circles + bias, data = d3_3)
vif(reg_3_d_id)
summary(reg_3_d_id)
reg_3_d <- lm(donation ~ ERQ + attitude_asylum + Recat..IOS.circles + bias, data = d3_3)
vif(reg_3_d)
summary(reg_3_d)
# model: dv~iv+cv
reg_3_p_emp_c <- lm(petition ~ ERQ + attitude_asylum + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_3)
vif(reg_3_p_emp_c)
summary(reg_3_p_emp_c)
reg_3_p_id_c <- lm(petition ~ Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_3)
vif(reg_3_p_id_c)
summary(reg_3_p_id_c)
reg_3_p_c <- lm(petition ~ ERQ + attitude_asylum + Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_3)
vif(reg_3_p_c)
summary(reg_3_p_c)
reg_3_d_emp_c <- lm(donation ~ ERQ + attitude_asylum + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_3)
vif(reg_3_d_emp_c)
summary(reg_3_d_emp_c)
reg_3_d_id_c <- lm(donation ~ Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_3)
vif(reg_3_d_id_c)
summary(reg_3_d_id_c)
reg_3_d_c <- lm(donation ~ ERQ + attitude_asylum + Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_3)
vif(reg_3_d_c)
summary(reg_3_d_c)
# condition 4: empathy + recat
reg_4_p_emp <- lm(petition ~ ERQ + attitude_asylum, data = d3_4)
vif(reg_4_p_emp)
summary(reg_4_p_emp)
reg_4_p_id <- lm(petition ~ Recat..IOS.circles + bias, data = d3_4)
vif(reg_4_p_id)
summary(reg_4_p_id)
reg_4_p <- lm(petition ~ ERQ + attitude_asylum + Recat..IOS.circles + bias, data = d3_4)
vif(reg_4_p)
summary(reg_4_p)
reg_4_d_emp <- lm(donation ~ ERQ + attitude_asylum, data = d3_4)
vif(reg_4_d_emp)
summary(reg_4_d_emp)
reg_4_d_id <- lm(donation ~ Recat..IOS.circles + bias, data = d3_4)
vif(reg_4_d_id)
summary(reg_4_d_id)
reg_4_d <- lm(donation ~ ERQ + attitude_asylum + Recat..IOS.circles + bias, data = d3_4)
vif(reg_4_d)
summary(reg_4_d)
# model: dv~iv+cv
reg_4_p_emp_c <- lm(petition ~ ERQ + attitude_asylum + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_4)
vif(reg_4_p_emp_c)
summary(reg_4_p_emp_c)
reg_4_p_id_c <- lm(petition ~ Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_4)
vif(reg_4_p_id_c)
summary(reg_4_p_id_c)
reg_4_p_c <- lm(petition ~ ERQ + attitude_asylum + Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_4)
vif(reg_4_p_c)
summary(reg_4_p_c)
reg_4_d_emp_c <- lm(donation ~ ERQ + attitude_asylum + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_4)
vif(reg_4_d_emp_c)
summary(reg_4_d_emp_c)
reg_4_d_id_c <- lm(donation ~ Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_4)
vif(reg_4_d_id_c)
summary(reg_4_d_id_c)
reg_4_d_c <- lm(donation ~ ERQ + attitude_asylum + Recat..IOS.circles + bias + BEconcern + democrat + republican + donate_year_yes + donate_life_yes + sign_year_yes + sign_life_yes, data = d3_4)
vif(reg_4_d_c)
summary(reg_4_d_c)
```

# Regression Plots
1. plot(modelname) for Residuals vs. fitted values/Q-Q plots/Scale Location plots/Cook’s distance plots
```{r}
# condition 1
plot(reg_1_p_emp)
plot(reg_1_p_id)
plot(reg_1_p)
plot(reg_1_d_emp)
plot(reg_1_d_id)
plot(reg_1_d)
```

```{r}
# condition 2
plot(reg_2_p_emp)
plot(reg_2_p_id)
plot(reg_2_p)
plot(reg_2_d_emp)
plot(reg_2_d_id)
plot(reg_2_d)
```

```{r}
# condition 3
plot(reg_3_p_emp)
plot(reg_3_p_id)
plot(reg_3_p)
plot(reg_3_d_emp)
plot(reg_3_d_id)
plot(reg_3_d)
```

```{r}
# condition 4
plot(reg_4_p_emp)
plot(reg_4_p_id)
plot(reg_4_p)
plot(reg_4_d_emp)
plot(reg_4_d_id)
plot(reg_4_d)
```
# Code for GGplots!! 
```{r}
```
#one example using boxplots

boxplot(d3$petition ~ d3$Condition,
        data=d3,
        ylab="activism willingness - petition", 
        xlab = "Condition")

boxplot(d3$donation ~ d3$Condition,
        data=d3,
        ylab="activism willingness - donation", 
        xlab = "Condition")
```{r}
```
