---
title: "code"
output: html_document
---

# Load packages + data
```{r}
library(tidyverse)
library(psych)
library(here)
library(lm.beta)

d <- read.csv(here("simulated_data.csv"))
```

# Data Cleaning
```{r}
#First step is to format the csv & delete entries that skipped to the end of the survey

d1 <- d[-(1:2),]
d1 <- d1 %>% 
  filter(Q1 == 1,
         Age != 1,
         US.resident == 1)

#!!threshold of completion minutes 
#!!NA value strategy

#Reverse code
d2 <- d1 %>% 
  mutate_at(c("Attitude...self_3", "Attitude...asylum_3","Attitude...self_5", "Attitude...asylum_5"),
            recode, "1" = 3, "2" = 2, "3" = 1)

d2 <- d2 %>% 
  mutate_at(c("BaseEmpathic.concern_2", "BaseEmpathic.concern_5", "BaseEmpathic.concern_6"),
            recode, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1)
         
#Recode to create new variables
d2[,17:71] <- d2[,17:71] %>% mutate_if(is.character, as.numeric)
sapply(d2,class)
# Basic Empathic Concern (BEconcern)
d3 <- d2
which(colnames(d3) == "BaseEmpathic.concern_1")
alpha(d3[, 27:33])
d3 <- d3%>% 
  mutate(
  BEconcern = rowMeans(select(., c("BaseEmpathic.concern_1", "BaseEmpathic.concern_2","BaseEmpathic.concern_3",
                                 "BaseEmpathic.concern_5", "BaseEmpathic.concern_6", "BaseEmpathic.concern_7"))))
# American Identity
which(colnames(d3) == "Identif..as.American_1")
alpha(d3[, 34:37])
d3 <- d3%>% 
  mutate(
  identity = rowMeans(select(., c("Identif..as.American_1", "Identif..as.American_2","Identif..as.American_3",
                                 "Identif..as.American_4"))))

#Petition Willingess 
which(colnames(d3) == "activism...petition_1")
alpha(d3[, 38:41])
d3 <- d3%>% 
  mutate(
  petition = rowMeans(select(., c("activism...petition_1", "activism...petition_2","activism...petition_3",
                                 "activism...petition_4"))))
#!!Activism Donation
which(colnames(d3) == "activism...donation_1")
alpha(d3[, 42:45])
d3 <- d3%>% 
  mutate(
  donation = rowMeans(select(., c("activism...donation_1", "activism...donation_2","activism...donation_3",
                                 "activism...donation_4"))))

#Empathy check: emotional response = ER
which(colnames(d3) == "Emp..Emot..Resp._1")
alpha(d3[, 47:52])
d3 <- d3%>% 
  mutate(
  attitude_asylum = rowMeans(select(., c("Emp..Emot..Resp._1", "Emp..Emot..Resp._2","Emp..Emot..Resp._3",
                                 "Emp..Emot..Resp._4", "Emp..Emot..Resp._5", "Emp..Emot..Resp._6"))))

#Attitude/Intergroup_Bias Self = attitude_self
which(colnames(d3) == "Attitude...self_1")
alpha(d3[, 54:59])
d3 <- d3%>% 
  mutate(
  attitude_self = rowMeans(select(., c("Attitude...self_1", "Attitude...self_2","Attitude...self_3",
                                 "Attitude...self_4", "Attitude...self_5", "Attitude...self_6"))))
#Basic Empathic Concern_asylum = EC_asylum
which(colnames(d3) == "Attitude...asylum_1")
alpha(d3[, 60:65])
d3 <- d3%>% 
  mutate(
  attitude_asylum = rowMeans(select(., c("Attitude...asylum_1", "Attitude...asylum_2","Attitude...asylum_3",
                                 "Attitude...asylum_4", "Attitude...asylum_5", "Attitude...asylum_6"))))


#Demographics - Control Variable
#Keep original: Age, gender, ethnicity, education, employment, region
#Dummy code: 
# political
d3 <- d3 %>% 
  mutate(
    democrat = if_else(Political == 1, 1, 0),
    republican = if_else(Political == 2, 1, 0),
    independent = if_else(Political == 3, 1, 0),
    somethingelse = if_else(Political == 5,1,0),
    dontknow = if_else(Political == 10,1,0)
  )
#previous activism engagement
d3 <- d3 %>% 
  mutate(
    donate_year_yes = if_else(previous.activism_1 == 1, 1, 0),
    donate_year_no = if_else(previous.activism_1 == 2, 1, 0),
    sign_year_yes = if_else(previous.activism_2 == 1, 1, 0),
    sign_year_no = if_else(previous.activism_2 == 2, 1, 0),
    donate_life_yes = if_else(previous.activism_3 == 1, 1, 0),
    donate_life_no = if_else(previous.activism_3 == 2, 1, 0),
    sign_life_yes = if_else(previous.activism_4 == 1, 1, 0),
    sign_life_no = if_else(previous.activism_4 == 2, 1, 0)
  )


```
# T-test
1. Each Condition * Control
2. Recat + Empathy * Empathy
3. Recat + Empathy * Recat
```{r}
```
# ANOVA: Compare Group Results
1. Post test dependent variables
2. Past activism behavior
3. Manipulation check scores
4. Baseline empathic concern
```{r}
#Compare Group Results: regressions vs ANOVAs - using petition as example DV
Control_and_ID <- d3 %>%
  filter(Condition == "1" | Condition == "2") %>%
  mutate_at(c("Condition"),
            recode, "1" = 0, "2" = 1)

Control_and_empathy <- d3 %>%
  filter(Condition == "1" | Condition == "3") %>%
    mutate_at(c("Condition"),
            recode, "1" = 0, "3" = 1)

Control_and_Emp_ID <- d3 %>%
  filter(Condition == "1" | Condition == "4") %>%
  mutate_at(c("Condition"),
          recode, "1" = 0, "4" = 1)

EmpONLY_vs_EmpANDID <- d3 %>%
  filter(Condition == "3" | Condition == "4") %>%
  mutate_at(c("Condition"),
          recode, "3" = 0, "4" = 1)

IdONLY_vs_EmpANDID <- d3 %>%
  filter(Condition == "3" | Condition == "4") %>%
  mutate_at(c("Condition"),
          recode, "2" = 0, "4" = 1)

#control versus each condition (ID only, emp only, ID+empahty)
reg_petition_1 <- lm(petition~Control_and_ID$Condition, data=Control_and_ID)

summary(reg_petition_1)

reg_petition_2 <- lm(petition~Control_and_empathy$Condition, data=Control_and_empathy)

summary(reg_petition_2)

reg_petition_3 <- lm(petition~Control_and_Emp_ID$Condition, data=Control_and_Emp_ID)

summary(reg_petition_3)

#ID+empathy versus ID only and Emp only
reg_petition_4 <-lm(petition~EmpONLY_vs_EmpANDID$Condition, data=EmpONLY_vs_EmpANDID)

summary(reg_petition_4)

reg_petition_5 <-lm(petition~IdONLY_vs_EmpANDID$Condition, data=IdONLY_vs_EmpANDID)

summary(reg_petition_5)

##aov(dv~X*Y,data=df)
##m1 <- lm(dv~X+Y,data=df)
##m2 <- lm(dv~X*Y,data=df
```
# Regression: 
1. check VIF for multicollinearity
2. models
3. plot(modelname) for Residuals vs. fitted values/Q-Q plots/Scale Location plots/Cook’s distance plots

This tutorial code seeme helpful
(https://datascienceplus.com/how-to-do-regression-analysis-for-multiple-independent-or-dependent-variables/)
```{r}
```
# Code for GGplots!! 
```{r}
```

```{r}
```
